---
output:
  html_document:
    toc: true
    toc_float: true
params:
  turnus: "Aug"
  kurz: "Ekonomie"
---

---
title: '`r paste0(params$kurz," (",params$turnus,")")`'
---

```{r init_course, include=FALSE}
library(knitr)
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=FALSE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

```{r}
source("library.r")
source("loadprocesseddata.r")
```

```{r dataset}
thiskurz <- kurzy %>% filter(session == as.character(params$turnus),
                             kurz == as.character(params$kurz))
```

# Course feedback

## Overall rating

```{r}
hodavg <- thiskurz %>% group_by(kurzslot) %>% summarise(prumer=mean(hodnoceni))
names(hodavg) <- c("Course block","Average rating (1 is best, 5 worst)")
```

Average rating: `r knitr::kable(hodavg, digits=2)`

(If you only taught in one slot and are seeing two, or vice versa, this is because of how the students input the data into the form.)

## What did they like best?

```{r results="asis"}
print_bullets(thiskurz$libilo,"en")
```

## What could be improved

```{r results="asis"}
print_bullets(thiskurz$zmenit,"en")
```

## How difficult was it?

### Course sessions

### Pre-Discover bundle

# Participation

# Tutor feedback

## Rating

## Remarks on/to the tutor

```{r results="asis"}
print_bullets(thiskurz$lektorpoznamky,"en")
```

# Impact

Did the course influence the students?

## Yes, no?

```{r}
ovlivneno <- thiskurz %>%
  filter(!is.na(ovlivnil)) %>% 
  mutate(ovlivnil = ifelse(ovlivnil %in% c("Ano","Yes"), 1, 0)) %>% 
  summarise(ovlivnil = mean(ovlivnil, na.rm=T))
```

```{r, results="asis",strip.white=T}
library(flexdashboard)
gauge(round(ovlivneno[1,1]*100, 0), min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```

## In what way?

```{r results="asis"}
print_bullets(thiskurz$ovlivnilVCem,"en")
```

## If not, why?

```{r results="asis"}
print_bullets(thiskurz$ovlivnilProcNe,"en")
```

